The Effects of Mandatory Seat Belt Laws on Driving Behavior and Traffic Fatalities

### 2024-08-23 paper.qmd
Add references.

---
title: "The Effects of Mandatory Seat Belt Laws on Driving Behavior and Traffic Fatalities"
author:
  - name: Juan David Rengifo-Castro
    orcid: 0009-0004-5169-4484
    email: jdrengifoc@eafit.com
    affiliations:
      - name: EAFIT
        city: Medellín
  - name: Angel Samuel Suesca Rios
    email: assuescar@eafit.edu.co
    affiliations:
      - name: Banco de la República
        city: Medellín
  - name: Mario Aguirre Posada
    email: maguirrep@eafit.edu.co
    affiliations:
      - name: EAFIT
        city: Medellín
format: html
editor: visual
---

@@

@@

>>>>

---
title: "The Effects of Mandatory Seat Belt Laws on Driving Behavior and Traffic Fatalities"
author:
  - name: Juan David Rengifo-Castro
    orcid: 0009-0004-5169-4484
    email: jdrengifoc@eafit.com
    affiliations:
      - name: EAFIT
        city: Medellín
  - name: Angel Samuel Suesca Rios
    email: assuescar@eafit.edu.co
    affiliations:
      - name: Banco de la República
        city: Medellín
  - name: Mario Aguirre Posada
    email: maguirrep@eafit.edu.co
    affiliations:
      - name: EAFIT
        city: Medellín
format: html
editor: visual
bibliography: references.bib
---

@@

**Provided literature:**

-   [@cohen2003]

-   [@stock2020introduction Exercise 10.2]

@@

**Data:** A panel of 50 U.S. states plus the District of Columbia from 1983 to 1997 [@data_usseatbelts].
